Active Code Completion

### 2012-03-20 icse12/graphite-icse12.tex
funding info. controlled user study -> pilot study

\begin{abstract}
Code completion menus have replaced standalone API browsers for most developers because they are more tightly  integrated into the development workflow. Refinements to the code completion menu that incorporate additional sources of information have similarly been shown to be valuable, even relative to standalone counterparts offering similar functionality. In this paper, we describe {\em active code completion}, a technique that enables the integration of a much broader array of interactive and highly-specialized code generation interfaces, called {\em palettes}, directly into the editor environment. Using several empirical methods, we examine the contexts in which such a system could be useful, describe the design constraints governing the system architecture as well as particular code completion interfaces, and design one such system, named Graphite, for the Eclipse Java development environment. Using Graphite, we implement a palette for writing regular expressions as our primary  example and conduct a controlled user study that provides further evidence in support of the claim that integrating specialized tools directly into the editor environment is both feasible, particularly if aided by an  active code completion system like Graphite, and valuable to professional developers.
\end{abstract}

@@

Finally, we conduct a controlled lab study with a more complex palette, implemented using Graphite, that assists  developers as they write regular expressions (Section 6). The data and observations gathered from this study provide  specific evidence in support of the broader claim that highly-specialized tools that are integrated directly with the editing environment are particularly useful, and that an active code completion system like Graphite makes developing, deploying and discovering such tools fundamentally simpler.

\section{Survey Results}
To validate our general conceptualization of active code completion, develop concrete design criteria and create a concrete list of use cases, we began by conducting a large survey of professional software developers.

@@

%\begin{figure}
%  \includegraphics[width=\linewidth]{mockup-palette-small.png}
%  \caption{An example mockup palette for regular expressions shown to the survey participants. In the survey, they were shown the surrounding Eclipse IDE together.}
%  \label{regex}
%\end{figure}
%
Next, we presented participants with a series of mockup palettes for a Color class (more complex than the one we ultimately implemented in Figure 1a), a regular expression class, and a SQL query class. Participants were also shown mockup screenshots demonstrating how a user could invoke the palette, and a mockup showing the code that would be inserted once a selection had been made. Before presenting each mockup, we gathered information about  the strategies that they would normally use to instantiate the class.

@@

fasdfahsdfjk asdf alsdfhjkasdfh alsdhkjfh asdkflahs dfkjahs djkfhkjadfjakshf kjhasjdf akskdjfha sdhfkja sdfhajksdfa hsdfkaj sdfhasdf ahdfkajsd fhasdjkfhjas dkfa dfkadfa
fasdfahsdfjk asdf alsdfhjkasdfh alsdhkjfh asdkflahs dfkjahs djkfhkjadfjak
% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

>>>>

\begin{abstract}
Code completion menus have replaced standalone API browsers for most developers because they are more tightly  integrated into the development workflow. Refinements to the code completion menu that incorporate additional sources of information have similarly been shown to be valuable, even relative to standalone counterparts offering similar functionality. In this paper, we describe {\em active code completion}, a technique that enables the integration of a much broader array of interactive and highly-specialized code generation interfaces, called {\em palettes}, directly into the editor environment. Using several empirical methods, we examine the contexts in which such a system could be useful, describe the design constraints governing the system architecture as well as particular code completion interfaces, and design one such system, named Graphite, for the Eclipse Java development environment. Using Graphite, we implement a palette for writing regular expressions as our primary  example and conduct a small pilot study that provides further evidence in support of the claim that integrating specialized tools directly into the editor environment is both feasible, particularly if aided by an active code completion system like Graphite, and valuable to professional developers.
\end{abstract}

@@

Finally, we conducted a pilot lab study with a more complex palette, implemented using Graphite, that assists developers as they write regular expressions (Section 6). The data and observations gathered from this study provide specific evidence in support of the broader claim that highly-specialized tools that are integrated directly with the editing environment are particularly useful, and that an active code completion system like Graphite makes developing, deploying and discovering such tools fundamentally simpler.

\section{Survey}
To validate our general conceptualization of active code completion, develop concrete design criteria and create a concrete list of use cases, we began by conducting a large survey of professional software developers.

@@

%\begin{figure}
%  \includegraphics[width=\linewidth]{mockup-palette-small.png}
%  \caption{An example mockup palette for regular expressions shown to the survey participants. In the survey, they were shown the surrounding Eclipse IDE together.}
%  \label{regex}
%\end{figure}
%
We presented participants with a series of mockup palettes for a Color class (more complex than the one we ultimately implemented in Figure 1a), a regular expression class, and a SQL query class. Participants were also shown mockup screenshots demonstrating how a user could invoke the palette, and a mockup showing the code that would be inserted once a selection had been made. Before presenting each mockup, we gathered information about  the strategies that they would normally use to instantiate the class.

@@

Funding for this work comes in part from the Korea Foundation for Advanced Studies (KFAS) and in part from NSF grant CCF-0811610. Any opinions, findings and conclusions or recommendations expressed in this material are those of the author(s) and do not necessarily reflect those of KFAS or the NSF.

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}
